Multi-scale trend analysis of water quality using error propagation of generalized additive models

### 2020-11-05 manu_draft.Rmd
text about moving window

We apply this method for windows of a chosen width of years.  This approach provide evaluates whether there is a significant linear trend in chlorophyll over a chosen series of years, by providing a more comprehensive assessment of all the data in those years (i.e., the seasonal averages, plus their uncertainty).  Some years may have had more sampling, resulting in smaller standard error for $\hmt$, while others may have had less sampling, result in higher standard error. The meta-analysis explicitly includes these differences in uncertainty magnitudes.

>>>>

We apply this method for windows of a chosen width of years.  This approach evaluates whether there is a significant linear trend in chlorophyll over a chosen series of years, by providing a more comprehensive assessment of all the data in those years (i.e., the seasonal averages, plus their uncertainty).  Some years may have had more sampling, resulting in smaller standard error for $\hmt$, while others may have had less sampling, result in higher standard error. The meta-analysis explicitly includes these differences in uncertainty magnitudes.

As a final analysis, the chosen windows for evaluating a trend for a selected seasonal average can be applied across the time series to assess periods of time within which trends could be significant or not.  Although the initial window width and seasonal period to evaluate is chosen by the analyst, applying the method in a moving window approach reduces some of the ambiguity around points in the time series when trends may be changing with reasonable certainty.  The moving window approach applies the meta-analysis model from left to right in the time series across the seasonal averages to obtain the slope and significance of the estimated trend.  We choose a centered window where the model estimates are based on results at equal half-window widths to the left and right of a given year.  Although a left- or right-centered window could also be applied, we limit the analysis to a centered window to demonstrate the concept.
